Incentivizing Exploration with Heterogeneous Utilities

### 2018-01-26 introduction.tex
divide the paper into sections

\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel}

\usepackage{blindtext}
\usepackage{amssymb}

\usepackage[]{algorithm}
\usepackage[]{algorithmic}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{xr} 
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsthm}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{dblfloatfix}
\usepackage{bbm}

\newcommand{\IE}{IE} 
\newcommand{\argmax}{\mathop{\mathrm{argmax}}}

\newcommand\floor[1]{\lfloor#1\rfloor}
\newcommand\ceil[1]{\lceil#1\rceil}

\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}

\title{Incentivizing Exploration with Heterogeneous Utilities}

\begin{document}

\maketitle

\section{Introduction}
In this paper, we study incentivizing exploration with heterogeneous agent preferences.
In this problem,   
arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities. Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.  Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.  To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.

@@

\section{Problem Setting}
\label{sec:prob}

We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
A stream of myopic selfish agents come to our system.  Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d. from a known distribution $F(\cdot)$ with compact support. We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''

Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.  The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.  Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.

At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$. In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector. For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.  We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.

This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.  In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).  Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.

We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$. Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$. 
As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.

To support later development, we define some additional notation.
We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random. We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e. $N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.

\section{Algorithm and Upper Bound}
\label{sec:ub}

In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior. We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.

\subsection{Our Algorithm}
Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
\begin{itemize}
\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
\item arm $i$ has not been played previously in the current round.
\end{itemize}
Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.

If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$. This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.  (We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).

We describe our algorithm in detail as follows:

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
  \IF {$S\setminus V$ is non-empty}
    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
  \ELSE
  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
  \ENDIF
  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
  \IF {$n\neq \min_{i}N(i,t)$} 
  	\STATE $V=\emptyset$
  \ENDIF
  \STATE Update the round number, $n = \min_{i} N(i,t)$
}\ENDFOR

\end{algorithmic}
\end{algorithm}

\subsection{Assumptions}
In this section, we state several assumptions assumed by our analysis.  First define
\begin{align}
\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
\end{align}
which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:

\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$. We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$. 
\label{A1}
\end{assumption}

As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite. Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.

\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
\label{A2}
\end{assumption}

We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.

\begin{assumption}
Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
\label{A3}
\end{assumption}

Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.

\subsection{General Results}

In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.  This is stated in the following pair of theorems, which together constitute our main results.

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
\label{rst:budget}
\end{theorem}

\begin{theorem}
The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
\label{rst:regret}
\end{theorem}

Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.  Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$. Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$. Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$. We know $p(0)=p$.

With this additional notation, we now prove several lemmas.
First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.

\begin{lemma}
$S(\delta)\leq M\delta$.
\label{lemma:sdelta}
\end{lemma}

\begin{proof}
\begin{align*}
S(\delta)
&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
&=M\delta.
\end{align*}
\end{proof}

The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.

\begin{lemma}
Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have 
\begin{align}
P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
\end{align}
for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

We need the following lemma in order to prove Lemma~\ref{round:prob}.

\begin{lemma}
For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
\begin{align}
\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{n0-inequality}
\end{lemma}

\begin{proof}
First, we observe that
\begin{align}
&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
\end{align}
Since $\log(x)\leq x-1$ for $x>0$, we know 
\begin{align}
\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
\end{align}

Thus, we know
\begin{align}
\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
\end{align}

To prove the lemma, we just need to show for $n\geq n_{0}$, we have
\begin{align}
\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
\end{align}
Inequality~(\ref{n0-equ}) is true because of the following two observations:
\begin{itemize}
\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
\end{itemize}

Thus, we know our lemma is true.

\end{proof}

To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.

\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$. We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$. If
\begin{align}
f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
\end{align}
then
\begin{align}
Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
\end{align}
\label{ACI-inequality}
\end{lemma}

We now prove Lemma~\ref{round:prob}.

\begin{proof}[Proof of Lemma~\ref{round:prob}]
In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$. If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
\begin{align}
&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
\end{align}
which means their myopic action would incur no regret.

Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
\begin{align}
&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
\end{align}

To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
\begin{align}
S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
\end{align}

Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
\begin{align}
\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}

Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}
Similarily, we can bound 
\begin{align}
&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
\end{align}

Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$. Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}

\end{proof}

Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.

\begin{lemma}
Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
\label{round:length}
\end{lemma}

\begin{proof}
	A round completes when each arm is pulled at least once in that round. Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled. Then we know 
\begin{equation*}
\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
\end{equation*}

Fix $i$. In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.  There are two ways a trial can be successful:
\begin{itemize}
\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one). In this case, the probability that the trial is succesful is $1$.  
\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$. In this case, the probability that the trial is successful is at least $n^{-1}$.
\end{itemize}

Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.  Thus,
\begin{align}
E[t_{n+1}-t_{n}]\leq Nn. \nonumber
\end{align}
\end{proof}

We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
\begin{lemma}
For all $n\geq 1$, we have
\begin{align}
0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{lemma:cal2}
\end{lemma}
\begin{proof}
\begin{align}
&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
\end{align}

Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$. It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum. Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$. Thus, our lemma holds true.
\end{proof}

Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.

\begin{proof}
Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$. Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$. Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$. For a fixed time $t$, define
\begin{align}
L^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
\end{align}
where $g(n,l)$ is a function which we will define later. Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$. We call $L[l](t)$ the $l^{th}$ envelope at time $t$. We often simplify the notation and use $L[l]$ instead of $L[l](t)$ without confusion.

In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$. Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by 
\begin{align}
&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
\leq & R + 2Wmg(n,l). \nonumber
\end{align}

Based on the above notations, we can rewrite the cumulative payment as follows:
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm. Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_2=\frac{2}{p}$. Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.

Thus,
\begin{align}
\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

Therefore,

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
\end{align}

We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
\begin{align}
&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})\right) \nonumber \\
=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber  \\
\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber
\end{align}

Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,

\begin{align}
&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\ 
=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
\end{align}

Based on Lemma~\ref{lemma:cal2}, we know
\begin{align}
&N(i,t)^{5/6}(l-1) \nonumber \\
=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
\end{align}

>>>>

\section{Introduction}

Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.

\begin{center}
\begin{tabular}{ c|c|c| } 
 \hline
     & Pulls arms directly & Needs to incentivize \\ 
\hline
 Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
 Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
 \hline
\end{tabular}
\end{center}

Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms. Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).   Problem settings correspond to cells and are described by the names C11, C12, and so on. An optimal algorithm for problem setting C11 has the best performance possible.

We wish to make two high-level points through this analysis:

\begin{itemize}
\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.  This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.  This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
\end{itemize}

In this paper, we study incentivizing exploration with heterogeneous agent preferences.
In this problem,   
arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities. Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.  Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.  To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.

@@
